Simulating cosmic variance in Weak Lensing: effects on parameter inferences

### 2015-12-04 Paper/paper.tex
mention psi bias before

\item Usually the true covariance is not known, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$. This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example). If we do that, and we do not correct for the $\bbh{\Psi}$ bias, the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value. In this case the bias sums up to 
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right)
\end{equation}

>>>>

\item Usually the true covariance is not known, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$. This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example). If we do that, and we do not correct for the $\bbh{\Psi}$ bias (see equation (\ref{firstmoment})), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value. In this case the bias sums up to 
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right)
\end{equation}
